Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-08-20 Manuscript/manuscriptPS.tex

\begin{tabular}{lccccccccc}

@@

POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13,kim16}  & 0.26  & 250 & 11190  & 53  & 298  & 200  & 180  & \citenum{POPC5POPS1withCaClCHARMM} \tabularnewline
POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13,kim16}  & 1.06  & 250 & 11174  & 214  & 298  & 200  & 180  & \citenum{POPC5POPS1with1MCaClCHARMM} \tabularnewline

@@

>>>>

\resizebox{0.87\textwidth}{!}{\begin{tabular}{lccccccccc}

@@

POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13} NBFIX 1 \cite{kim16}  & 0.26  & 250 & 11190  & 53  & 298  & 200  & 180  & \citenum{POPC5POPS1withCaClCHARMM} \tabularnewline
POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13} NBFIX 1 \cite{kim16}  & 1.06  & 250 & 11174  & 214  & 298  & 200  & 180  & \citenum{POPC5POPS1with1MCaClCHARMM} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 250  & 11207  & 0  & 320  & 400  & 300  & \citenum{POPC5POPS1CHARMMwithNBfixHan} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13} NBFIX 2 \cite{han2018graph}  & 0.14  & 250 & 11190  & 28  & 320  & 440  & 300  & \citenum{POPC5POPS1CHARMMwithNBfixHan} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13} NBFIX 2 \cite{han2018graph}  & 0.94  & 250 & 11174  & 189  & 320  & 440  & 300  & \citenum{POPC5POPS1CHARMMwithNBfixHan} \tabularnewline

@@

\end{tabular}}
